Sound Automated Synthesis of Digital Controllers

### 2016-10-12 paper/paper.tex
review introduction

Modern implementations of embedded control have proliferated with the
availability of low cost devices that can perform simple tasks for linear
control, spanning many areas such as environmental control and robotic
manipulations~\cite{astrom1997computer,Franklin15}.  The downside to this
approach is that in order to achieve low prices, devices are often limited
in their capabilities, be it a low number of gates in an FPGA or short word
lengths for microcontrollers.  In most cases a floating-point implementation
is not feasible and the system can benefit from the added resolution of a
fixed-point representation.  The ubiquity of these devices requires that
they have a robust design that ensures the correct behaviour in a number of
different environments.
%
% For this reason it is
% necessary to provide design tools that formally verify the correctness
% of the digital controller.

There has been previous work to formally verify uncertain linear systems
stability in digital controllers with considerations to the implementation
aspects ({\it i.e.}, fixed-point arithmetic and word-length)~\cite{Bessa16}. 
In particular, Bessa {\it et al.} considers finite-word length (FWL) effects
over digital controllers and also parameter uncertainties in the context of
verifying the (so-called) robust non-fragile
stability~\cite{bhattacharyya97}.  However, the authors do not consider the
compete range of approximations, related to time discretisation, and
quantisation effects.  As a result, the stability verification method
proposed by Bessa {\it et al.} is incomplete, given that false alarms can be
produced due to the quantisation effects.  Additionally, the authors do not
find a parametric solution for a digital controller given as a continuous
plant specification, in order to synthesize the controller implementation.

In this paper, however, we explore the automatic synthesis of {\em
correct-by-construction} dgital controllers, which reduces the deveopment
cost and design time for a number of models.  In particular, we are
interested in synthesising controllers for {\em hybrid closed-loop systems},
{\it i.e.}, embedded controllers along with a model of their physical
environment (the plant), which are {\em stable}.  Due to the complexity of
such systems, we focus on linear models with known configurations to perform
parametric synthesis of the controller dynamics.

Since the digital control synthesis is performed over a hybrid model, where
the plant displays a continuous behaviour and the controller operates in
both discrete time and state-space, we initially translate the problem into
a single domain which represents a bi-simulation of the original dynamics. 
Given our primary interest in evaluating digital effects in addition to
stability, we have modeled a digital equivalent of the plant by evaluating
the effects of the quantisers (A/D and D/A converters) as time
discretisation elements with quantisation noise.  The resulting closed loop
system is a program loop working over bit-vectors of fixed-point arithmetic
with fixed word length.  \blue{The deterministic effect of the FWL is considered
and quantization errors are included in the model as a additive uncertainty 
which must be taken into account for the correct synthesis of the robust controller
for linear systems with parametric uncertainties.}

>>>>

Modern implementations of embedded control have proliferated with the
availability of low cost devices that can perform simple tasks for linear
control, spanning many areas such as environmental control and robotic
manipulations~\cite{astrom1997computer,Franklin15}.  The downside to this
approach is that in order to achieve low prices, devices are often limited
in their capabilities, be it a low number of gates in an FPGA or short word
lengths for microcontrollers.  In most cases, a floating-point implementation
is not feasible and the system can benefit from the added resolution of a
fixed-point representation.  The ubiquity of these devices requires that
they have a robust design that ensures the correct behaviour in a number of
different environments.
%
% For this reason it is
% necessary to provide design tools that formally verify the correctness
% of the digital controller.

There has been previous work to formally verify uncertain linear systems
stability in digital controllers with considerations to the implementation
aspects ({\it i.e.}, fixed-point arithmetic and word-length)~\cite{Bessa16}. 
In particular, Bessa {\it et al.} consider finite-word length (FWL) effects
over digital controllers and also parameter uncertainties in the context of
verifying the (so-called) robust non-fragile
stability~\cite{bhattacharyya97}.  However, the authors do not consider the
compete range of approximations, related to time discretisation, and
quantisation effects.  As a result, the stability verification method
proposed by Bessa {\it et al.} is incomplete, given that false alarms can be
produced due to quantisation effects.  Additionally, the authors do not
find a parametric solution for a digital controller given as a continuous
plant specification, in order to synthesize the controller implementation.

Our work makes two major contributions. First, we explore the automatic synthesis 
of {\em correct-by-construction} digital controllers, which reduces the development
cost and design time for a number of models.  In particular, we are
interested in synthesising controllers for {\em hybrid closed-loop systems},
{\it i.e.}, embedded controllers along with a model of their physical
environment (the plant), which are {\em stable}.  Due to the complexity of
such systems, we focus on linear models with known configurations to perform
parametric synthesis of the controller dynamics.

Second, since the digital control synthesis is performed over a hybrid model, 
where the plant displays a continuous behaviour and the controller operates in
both discrete time and state-space, we initially translate the problem into
a single domain, which represents a bi-simulation of the original dynamics. 
Given our primary interest in evaluating digital effects in addition to
stability, we have modeled a digital equivalent of the plant by evaluating
the effects of the quantisers (A/D and D/A converters) as time
discretisation elements with quantisation noise.  The resulting closed loop
system is a program loop working over bit-vectors of fixed-point arithmetic
with fixed word length.  The deterministic effect of the FWL is considered
and quantization errors are included in the model as an additive uncertainty, 
which must be taken into account for the correct synthesis of the robust controller
for linear systems with parametric uncertainties.
